Blame and Coercion: Together Again for the Second Time

### 2019-10-17 paper.tex
4.1 effCEK

This section presents our second contribution, a framework for proving 
correctness of cast representations.
In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of semantics (in the style of CEK machines) indexed by cast representations ($ 
C $). 
In subsection~\ref{secc:framework:bisim}, we prove when $ C $ is 
$ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
\judgeSeval{C}{e}{o} $, that is, every $ surely \text{\lazyD} $ cast 
representation respects the \lazyD\ cast calculus. 
Proving a similar theorem for \lazyUD\ is in progress.

@@

We define cast representations and \effCEK{C}

space-efficient CEK abstract 
machine. This machine is parameterized over \emph{cast representation}.

\begin{definition}[Monoidic Cast Representation]
	A cast representation is monoidic if 
	for all $c : T_1 \Longrightarrow T_2$,
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c) = c$,
		\item $seq(c,id(T_2)) = c$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{definition}

@@

\figref{machine-cekcc} defines the machine. 
Let $ v $ range over value. A value is either the unit value, function, pair, 
left injection of sum, right injection of sum, and injection to $ \TOOdyn $.
Cast results ($ r $) and machine states ($ s $) are as before. 
Let $ \kappa $ range over continuations and let $ k $ range over 
pre-continuations. 
A continuation is now a pair where the first part is a cast and the second 
part is a pre-continuation. 
Pre-continuation are like the continuations before.

We list a fraction of reduction rules due to space limitation.
When values are constructed, their hypercoercion parts are filled with outputs 
of $ id $. For instance, when a function value is constructed, its first part 
and last part are initialized to $ id(T_1) $ and $ id(T_2) $ respectively.
When evaluating a cast expression, the current continuation is extended with a 
hypercoercion constructed by $ cast $. $ ext $ composes the new hypercoercion 
with the hypercoercion on the top of the continuation.
When evaluating a compound expression, the machine firstly construct the new 
pre-continuation, then turn it to a continuation by adding an identity 
hypercoercion at the top. For instance, when evaluating a \texttt{cons} 
expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
the new pre-continuation, then call $ cont $, which adds an identity cast to 
form a continuation. 
When a function call happens, the machine firstly cast the operand. If the 
casting succeeds, the machine then evaluate the body in the extended 
environment and the extended continuation. If the casting fails, the machine 
then halts with the blame label.

>>>>

This section presents our second contribution, a framework for proving 
correctness of cast representations.
In subsection~\ref{ssec:framework:cek}, we introduce \effCEK{C}, a family 
of space-efficient semantics (in the style of CEK machines) indexed by cast 
representations ($ C $). 
In subsection~\ref{secc:framework:bisim}, we prove when $ C $ is 
$ surely \; \text{\lazyD} $, $ \judgeDeval{e}{o} $ if and only $ 
\judgeSeval{C}{e}{o} $, that is, every $ surely \text{\lazyD} $ cast 
representation respects the \lazyD\ cast calculus. 
Proving a similar theorem for \lazyUD\ is in progress.

Our space-efficient CEK machine is parameterized over \emph{cast 
	representations}.

Some cast representations are monoids as well. They are useful in our 
correctness proof.

\begin{definition}[Monoid]
	A cast representation is a monoid if 
	for all $c : T_1 \Longrightarrow T_2$,
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c) = c$,
		\item $seq(c,id(T_2)) = c$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{definition}

@@

@@

\figref{machine-cekcc} defines the space-efficient CEK machine \effCEK{C}. This 
machine is similar to \ineffCEK{}. 
The most important differences are in values and continuations.
In \ineffCEK\, we have one value constructor for all casted value.
In \effCEK{C}, however, we do not have this generic value constructor, 
instead we push those casts into the value constructors most of the time and 
use $ \hcvOOinj{P}{v} $ to construct values injected to $ \TOOdyn $.
Non-casted values in \ineffCEK\ correspond to values in \effCEK{C} where the 
casts are identity (i.e. constructed by $ id(T) $).
In \ineffCEK\, a continuation have zero or more casts at the top.
In \effCEK{C}, however, every continuation has exactly one cast at the top.
Continuations in \ineffCEK\ that have no casts at the top correspond to 
continuations in \effCEK{C}\ whose casts are identity.
And continuations in \ineffCEK\ that have many casts at the top correspond to 
continuations in \effCEK{C}\ where those casts are composed by $ 
seq(c,c) $.

Let $ v $ range over value. A value is either the unit value, function, pair, 
left injection of sum, right injection of sum, and injection to $ \TOOdyn $.
Cast results ($ r $) and machine states ($ s $) are as before. 
Let $ \kappa $ range over continuations and let $ k $ range over 
pre-continuations. 
A continuation is now a pre-continuation capped with a cast.
Pre-continuation are like the continuations in \ineffCEK.

\todo[inline]{KC needs to describe added rules. -KC}
We list a fraction of reduction rules due to space limitation.
When values are constructed, their hypercoercion parts are filled with outputs 
of $ id $. For instance, when a function value is constructed, its first part 
and last part are initialized to $ id(T_1) $ and $ id(T_2) $ respectively.
When evaluating a cast expression, the current continuation is extended with a 
hypercoercion constructed by $ cast $. $ ext $ composes the new hypercoercion 
with the hypercoercion on the top of the continuation.
When evaluating a compound expression, the machine firstly construct the new 
pre-continuation, then turn it to a continuation by adding an identity 
hypercoercion at the top. For instance, when evaluating a \texttt{cons} 
expression, the machine firstly construct $ \hckOOconsI{e_2}{\rho}{\kappa} $, 
the new pre-continuation, then call $ cont $, which adds an identity cast to 
form a continuation. 
When a function call happens, the machine firstly cast the operand. If the 
casting succeeds, the machine then evaluate the body in the extended 
environment and the extended continuation. If the casting fails, the machine 
then halts with the blame label.
